\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-23 main.tex

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{examples/images/squid-susc-simulation.pdf}
    \caption{Simulation of a scanning SQUID susceptometry measurement. a) Geometry of the \inline{Device} representing the ``sensor'' SQUID. b) Geometry of the \inline{Device} representing the ``sample'' SQUID. c) Susceptibility of the sample SQUID measured at a temperature of 4.0 K. d) Simulated susceptibility assuming a vertical distance of 50 nm between the surfaces of the two SQUID chips. The pickup loop of the sample, which in reality is connected to a SQUID circuit that has a non-linear magnteic response, is modeled as a continuous superconducting loop in the $n=0$ fluxoid state (i.e. Meissner state). The scale bar in (a) applies to all four panels.}
    \label{fig:squid-susc}
\end{figure}
